Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-27 manuscript.tex

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-illinoisdatabankIDB-2796521}{}%
Althaus, S., Bajjalieh, J., Carter, J., Peyton, B., \& Shalmon, D. (2020). \emph{Cline center historical phoenix event data. Cline center for advanced social research. V1.3.0. May 4} {[}Data set{]}. University of Illinois at Urbana-Champaign. \url{https://doi.org/10.13012/B2IDB-0647142_V3}

\leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
Boschee, E., Lautenschlager, J., O'Brien, S., Shellman, S., Starz, J., \& Ward, M. (2015). \emph{ICEWS Coded Event Data} (Version V27) {[}Data set{]}. Harvard Dataverse. \url{https://doi.org/10.7910/DVN/28075}

@@

\leavevmode\hypertarget{ref-wang2016growing}{}%
Wang, W., Kennedy, R., Lazer, D., \& Ramakrishnan, N. (2016). Growing pains for global monitoring of societal events. \emph{Science}, \emph{353}(6307), 1502--1503.

@@

\hypertarget{appendix-a}{%
\section{Appendix A}\label{appendix-a}}

Given the inherent issues found in event data sets (Wang, Kennedy, Lazer, \& Ramakrishnan, 2016), we conducted the same analyses on the Cline Center Historical Phoenix Event Data (Althaus, Bajjalieh, Carter, Peyton, \& Shalmon, 2020). After filtering for Syria as the target country and creating the count variables for all, positive, and negative events each day, there was not enough variability to transform the data into deciles. As a results, sextiles were used for these analyses. For comparison, the filtered ICEWS data was also transformed into sextiles.

\hypertarget{crqa-for-phoenix-data-in-sextiles}{%
\subsection{CRQA for Phoenix data in sextiles}\label{crqa-for-phoenix-data-in-sextiles}}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only Phoenix data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 29.441 & 0.617 & & 38.232 & 0.000 & *** & 30.792 & 0.332 &\tabularnewline
NRLINE & 140.000 & 0.457 & & 168.000 & 0.000 & *** & 141.000 & 0.450 &\tabularnewline
maxL & 4.000 & 0.443 & & 5.000 & 0.088 & . & 4.000 & 0.454 &\tabularnewline
L & 2.143 & 0.894 & & 2.292 & 0.014 & * & 2.234 & 0.165 &\tabularnewline
ENTR & 0.420 & 0.904 & & 0.683 & 0.012 & * & 0.569 & 0.239 &\tabularnewline
rENTR & 0.382 & 0.750 & & 0.492 & 0.171 & & 0.518 & 0.096 & .\tabularnewline
LAM & 31.600 & 0.350 & & 42.105 & 0.042 & * & 29.619 & 0.625 &\tabularnewline
TT & 2.252 & 0.247 & & 2.356 & 0.142 & & 2.295 & 0.314 &\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target Phoenix data.}\tabularnewline
CRQ analyses for sextiled Phoenix event data found increased levels of coupling between positive events and social cohesion, irrespective of target or source and target filtering. Negative events were not coupled with social cohesion irrespective of filtering.
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 32.677 & 0.069 & . & 37.313 & 0.000 & *** & 31.610 & 0.130 &\tabularnewline
NRLINE & 152.000 & 0.047 & * & 160.000 & 0.000 & *** & 145.000 & 0.133 &\tabularnewline
maxL & 4.000 & 0.465 & & 7.000 & 0.001 & *** & 4.000 & 0.448 &\tabularnewline
L & 2.184 & 0.577 & & 2.344 & 0.000 & *** & 2.193 & 0.476 &\tabularnewline
ENTR & 0.507 & 0.550 & & 0.751 & 0.000 & *** & 0.523 & 0.446 &\tabularnewline
rENTR & 0.462 & 0.289 & & 0.466 & 0.247 & & 0.476 & 0.214 &\tabularnewline
LAM & 40.453 & 0.051 & . & 50.746 & 0.001 & *** & 32.008 & 0.453 &\tabularnewline
TT & 2.446 & 0.044 & * & 2.217 & 0.376 & & 2.284 & 0.327 &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{crqa-for-icews-data-in-sextiles}{%
\subsection{CRQA for ICEWS data in sextiles}\label{crqa-for-icews-data-in-sextiles}}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for target only ICEWS data.}\tabularnewline
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 38.636 & 0.000 & *** & 36.759 & 0.001 & *** & 36.858 & 0.000 & ***\tabularnewline
NRLINE & 175.000 & 0.000 & *** & 165.000 & 0.001 & *** & 161.000 & 0.002 & **\tabularnewline
maxL & 5.000 & 0.079 & . & 4.000 & 0.438 & & 6.000 & 0.013 & *\tabularnewline
L & 2.234 & 0.148 & & 2.255 & 0.086 & . & 2.317 & 0.003 & **\tabularnewline
ENTR & 0.596 & 0.131 & & 0.623 & 0.088 & . & 0.723 & 0.002 & **\tabularnewline
rENTR & 0.430 & 0.450 & & 0.567 & 0.047 & * & 0.449 & 0.394 &\tabularnewline
LAM & 42.984 & 0.035 & * & 37.846 & 0.096 & . & 39.625 & 0.062 & .\tabularnewline
TT & 2.254 & 0.228 & & 2.471 & 0.036 & * & 2.373 & 0.081 & .\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}cccccccccc@{}}
\caption{CRQA results for source and target ICEWS data.}\tabularnewline
CRQ analyses for sextiled ICEWS event data found coupling between both positive and negative events with social cohesion, irrespective of target or source and target filtering. Negative events were more strongly coupled with social cohesion than positive events for the target only analyses.
The abscence of coupling between negative events and social cohesion in the Phoenix CRQ analyses speaks to the unreliability of event data, and that nonlinear analyses in general are only as valuable as the quality of the data being used.
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endfirsthead
\toprule
metric & all events & p & sig. & positive events & p & sig. & negative events & p & sig.\tabularnewline
\midrule
\endhead
DET & 32.840 & 0.061 & . & 37.451 & 0.000 & *** & 38.741 & 0.000 & ***\tabularnewline
NRLINE & 145.000 & 0.208 & & 166.000 & 0.001 & *** & 173.000 & 0.000 & ***\tabularnewline
maxL & 5.000 & 0.084 & . & 5.000 & 0.093 & . & 7.000 & 0.002 & **\tabularnewline
L & 2.297 & 0.007 & ** & 2.283 & 0.017 & * & 2.277 & 0.026 & *\tabularnewline
ENTR & 0.693 & 0.005 & ** & 0.667 & 0.016 & * & 0.632 & 0.058 & .\tabularnewline
rENTR & 0.500 & 0.128 & & 0.481 & 0.180 & & 0.393 & 0.724 &\tabularnewline
LAM & 34.221 & 0.208 & & 41.996 & 0.034 & * & 41.003 & 0.037 & *\tabularnewline
TT & 2.239 & 0.276 & & 2.348 & 0.107 & & 2.279 & 0.231 &\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{windowed-crqa-for-phoenix-data-in-sextiles}{%
\subsection{Windowed CRQA for Phoenix data in sextiles}\label{windowed-crqa-for-phoenix-data-in-sextiles}}

\hypertarget{syria-as-target-4}{%
\subsubsection{Syria as Target}\label{syria-as-target-4}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-pheonix}
\end{figure}

\hypertarget{syria-as-source-and-target-4}{%
\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-4}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-pheonix}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/pheonix/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-pheonix}
\end{figure}

\hypertarget{windowed-crqa-for-icews-data-in-sextiles}{%
\subsection{Windowed CRQA for ICEWS data in sextiles}\label{windowed-crqa-for-icews-data-in-sextiles}}

\hypertarget{syria-as-target-5}{%
\subsubsection{Syria as Target}\label{syria-as-target-5}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from target filtered data.}\label{fig:plot-RR-targ-all-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from target filtered data.}\label{fig:plot-DET-targ-all-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from target filtered data.}\label{fig:plot-RR-targ-pos-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from target filtered data.}\label{fig:plot-DET-targ-pos-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from target filtered data.}\label{fig:plot-RR-targ-neg-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from target filtered data.}\label{fig:plot-DET-targ-neg-secondary-icews}
\end{figure}

\hypertarget{syria-as-source-and-target-5}{%
\subsubsection{Syria as Source and Target}\label{syria-as-source-and-target-5}}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-RR-source-targ-all-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_all_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of all events from source and target filtered data.}\label{fig:plot-DET-source-targ-all-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-RR-source-targ-pos-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_pos_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of positive events from source and target filtered data.}\label{fig:plot-DET-source-targ-pos-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_RR} \caption{Windowed CRQA visualization of RR for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-RR-source-targ-neg-secondary-icews}
\end{figure}

\begin{figure}
\includegraphics[width=4in]{./results/secondary/icews/windowed-crqa/source_target/windowed_neg_DET} \caption{Windowed CRQA visualization of DET for social cohesion and count of negative events from source and target filtered data.}\label{fig:plot-DET-source-targ-neg-secondary-icews}
\end{figure}

>>>>

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-DVNux2f28075_2015}{}%
Boschee, E., Lautenschlager, J., O'Brien, S., Shellman, S., Starz, J., \& Ward, M. (2015). \emph{ICEWS Coded Event Data} (Version V27) {[}Data set{]}. Harvard Dataverse. \url{https://doi.org/10.7910/DVN/28075}

@@

@@
